Compositional Certified Resource Bounds

### 2015-04-14 paper/main.tex
fix wrong limitation

\authorinfo
{Quentin Carbonneaux \and Jan Hoffmann \and Zhong Shao}
{Yale University}
{\{quentin.carbonneaux, jan.hoffmann, zhong.shao\}@yale.edu}

@@

Our implementation does not currently support
all of Clight.  Programs with function pointers, goto statements,
continue statements, and dereferences of stack-allocated variables
cannot be analyzed automatically.  While these limitations concern the
current implementation, our technique is in principle capable to handle
them.

>>>>

\authorinfo
{Quentin Carbonneaux \and Jan Hoffmann \and Zhong Shao}
{Yale University, USA}
{\{quentin.carbonneaux, jan.hoffmann, zhong.shao\}@yale.edu}

@@

Our implementation does not currently support
all of Clight.  Programs with function pointers, goto statements,
continue statements, and pointers to stack-allocated variables
cannot be analyzed automatically.  While these limitations concern the
current implementation, our technique is in principle capable to handle
them.
